Influence of Connectivity on Dung Beetle Communities

### 2025-06-18 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
update for eric with some edits and assignment for tomorrow

---
title: "Influence of Connectivity on Dung Beetle Communities"
author: "ERIC ESCOBAR-CHENA"

# date: "\\vspace{-1em}"
header-includes:
 # - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
 - \usepackage{lineno}
 - \linenumbers
 - \usepackage[default]{sourcesanspro}
 - \usepackage{fancyhdr} # modify header into left, center, right
 - \pagestyle{fancy} # cues the use of fancy headers
 - \fancyfoot{} # cues the use of fancy footer
 - \fancyhead[L]{EEC MS Thesis Draft} # month & year on header left 
 - \fancyhead[R]{p. \thepage} # name and page on header right
 - \usepackage{subcaption}
 - \usepackage{float}
# # - \fancyfoot[R]{ }
 - \usepackage{setspace}
 # - doublespacing # manipulate line spacing 
# - \usepackage{parskip} # manipulate indents and spacing before/after paragra phs 
# - \usepackage{xcolor} # changes colors of text
# # http://latexcolor.com/ to choose colors
# # define the colors used above with rgb codes
# - \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
# - \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
# # to center to top level (#) headings (my name) and change color of font
# # more info # https://www.ctan.org/pkg/sectsty
# - \usepackage{sectsty}
# - \sectionfont{\centering\color{darkmidnightblue}}
# # to center to sub-sub-headings (###) and change color of font
# - \usepackage{sectsty} 
# - \subsectionfont{\centering\color{darkmidnightblue}}
# - \usepackage{sectsty} 
# - \subsubsectionfont{\raggedright\color{darkmidnightblue}}
# - \usepackage{wrapfig} 
# - \newcommand{\blandscape}{\begin{landscape}}
# - \newcommand{\elandscape}{\end{landscape}}
# - \usepackage[font=small,labelfont=bf]{caption} #Required for specifying captions to tables and figures
# - \usepackage{indentfirst}
# - \setlength\parindent{22pt} # uncomment if you want indented paragraphs
bibliography: ["eric-thesis.bib"]
output:
  pdf_document:
    includes:
      # in_header: style/preamble.tex
      template: null
      keep_tex: no
      extra_dependencies: ["float"]
      # number_sections: true
# documentclass: style/nsf2
biblio-style: apalike
csl: ecology.csl
---

@@

@@

2025
\newpage

@@

_Your dedication is typed here. It should begin with the word “To.”
(To my Mom is a typical dedication) If your dedication is longer than a single line it should be single-spaced, and centered vertically and horizontally_

@@

ACKNOWLEDGMENTS
_Acknowledgments must be written in complete sentences. Do not use direct address. For example, instead of Thanks, Mom and Dad!, you should say I thank my parents._

@@

LIST OF ABBREVIATIONS

A word to be defined: Write the definition here.

Another word:	Another def.

Another word:	Another def.

@@

@@

## CHAPTER 1

## TITLE OF CHAPTER ONE

@@

Dung beetles have emerged as a model system with which to test spatial ecology hypotheses [@ros_how_2012; @roslin_dung_2000].They are an incredibly well studied group of insects which are well known for driving a multitude of ecosystem functions [@hasan_dung_2024]. The removal, breakdown, and burial of animal feces drive important ecosystem interactions provided by dung beetles enhancing nutrient cycling and soil quality, the reduction of breeding sites for parasites, and a reduction in methane emissions from dung [@slade_disentangling_2016; @WOS:000350444300013]
Here, we aim to gain an understanding of how dung beetles, a group of insects well known for strong dispersal ability in order to compete for ephemeral resources [@hanski_dung_1991], interact with corridors in their landscapes.

We sampled dung beetle communities in experimental landscapes developed for the express purposes of comparing connected and isolated patches, as well as the effects of patch area to edge ratio and distance to edge [@tewksbury_corridors_2002]. To ask the questions: (1) How are species abundances of dung beetles distributed within isolated and connected patches and what are their relationships with assemblages in matrix habitat? (2) Does species richness vary when movement between patches is facilitated by movement corridors? (3) Are there shifts in species diversity/composition and what are the implications for ecosystem service functionality?

@@

Our study took place at the Savannah River Site (SRS), a National Environmental Research Park in southern South Carolina, US (33.208$^\circ$ N, 81.408$^\circ$ W) in four of seven experimental landscapes designed for the purposes of directly observing the impacts of corridors and patch shape on the movements of plants and animals [@tewksbury_corridors_2002]. Each experimental landscape, termed blocks, consists of four patches of open habitat around a central patch all together within a matrix of pine savanna. In each block the central patch (100 $\times$ 100 m) is always connected to one peripheral patch with identical dimensions by a 150 $\times$ 25 m corridor, this will hereafter be referred  to as the connected patch. The remaining patches are either "winged" or "rectangular".  The winged patch is also 100 $\times$ 100 m, however they exhibit their characteristic wings in the form of two 75 $\times$ 25 m offshoots meant to account for the extra area and edge space the corridor provides. The rectangular patch is 100 $\times$ 137.5 m also the same area as the space of the connected patch plus the corridor. Each block has a duplicate of either the winged or rectangle patch, all peripheral patches being 150 m from the center patch. For this study sampling was done in one of each patch type and in one matrix plot per block, all matrix blocks were set up 150 m away from the center as well.

@@

In the months of July and August 2024 dung beetles were sampled in 4 blocks spread across SRS, baited pitfall traps were placed in one of each patch type and in one matrix plot per block. Traps were placed in groups of 3 in the centers of each patch approximately 250 meters from the midpoint of the central patch 40 m from patch edge. Pitfalls were oriented in a triangular pattern with the bottom two traps positioned towards the center patch, each trap 20 m apart. Plots in the matrix were set up in a similar fashion with the center point 250 m from the center placed equidistant between adjacent patches. Individual pitfall traps consisted of two components, a 10cm tall by 8 cm wide cylinder base topped with a funnel with a 10cm wide rim. We sourced pig feces from the University of Florida Swine Barn Unit. Bait was processed into 5cm wide balls and wrapped in a layer of coffee filter material. For each sample period, traps were buried flush with the ground and baited with pig dung between 8-9 pm and picked up 12 hours later, all beetles captured were stored in ethanol for further processing. In total 16 sampling rounds were carried out with 4 rounds per block, 196 samples were collected.

@@

### Overview: Community Composition and Abundance

@@

@@

### Species Richness

@@

### Species Diversity

We used linear mixed-effects models to compare the influence of patch type on both Shannon Diversity and Simpson's indexes, including block as a random effect to account for spatial variation. In both models, the reference level for patch type was Connected.

@@

_Don't repeat results...tell us:

@@

_here look at other srs papers and see whats going on with edges_.

@@

\newpage
```{r Table1, echo=FALSE,message = FALSE,warning=FALSE}
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

@@

```{r Table2, echo=FALSE,message = FALSE,warning=FALSE}
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

@@

```{r Table 3, echo=FALSE,message = FALSE,warning=FALSE}
btl_spec_patch<- btl_data |>
  pivot_longer(pvin:osyl, names_to = "species", values_to = "n") |>
  group_by(species,patch) |>
  summarise(n=sum(n, na.rm=TRUE)) |>
  arrange(patch,desc(n)) |>
  pivot_wider(values_from=n,names_from=species) |>
  mutate(patch=case_when(
    patch == "c" ~ "Corridor",
    patch == "m" ~ "Matrix",
    patch == "w" ~ "Winged",
    patch == "r" ~ "Rectangle",
    .default = as.character(patch))) |>
  column_to_rownames("patch")

@@

```{r Table bray_patches, echo=FALSE,message = FALSE,warning=FALSE}

@@

```{r Table aovMO, echo=FALSE,message = FALSE,warning=FALSE}
aovM0<-read_csv(here("corridor_docs","eric_ms_thesis","tables","aovM0.csv")) %>%
# aovM0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM0
```

```{r Table MO, echo=FALSE,message = FALSE,warning=FALSE}
M0<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M0.csv")) %>%
# M0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M0
```

```{r Table aovMO3, echo=FALSE,message = FALSE,warning=FALSE}
aovM3<-read_csv(here("corridor_docs","eric_ms_thesis","tables","aovM3.csv")) %>%
# aovM3<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM3.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM3
```

```{r Table M3, echo=FALSE,message = FALSE,warning=FALSE}
M3<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M3.csv")) %>%
# M3<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M3.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M3
```

```{r Table M_rich, echo=FALSE,message = FALSE,warning=FALSE}
M_rich<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_rich.csv")) %>%
# M_rich<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_rich.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Richness Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_rich
```

```{r Table M_shan, echo=FALSE,message = FALSE,warning=FALSE}
M_shan<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_shan.csv")) %>%
# M_shan<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_shan.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Shannon Diversity Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_shan
```

```{r Table M_simp, echo=FALSE,message = FALSE,warning=FALSE}
M_simp<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_simp.csv")) %>%
# M_simp<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_simp.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Simpson's Index Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_simp
```

@@

_A biographical sketch is required of all candidates. The biographical sketch should be in narrative form. Third person, past tense, it typically includes the educational background of the candidate. The author should have replaced this paragraph with their own._

>>>>

---
title: "Influence of Connectivity on Dung Beetle Communities"
author: "ERIC ESCOBAR-CHENA"
# date: "\\vspace{-1em}"
header-includes:
 # - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
 - \usepackage{lineno}
 - \linenumbers
 - \usepackage[default]{sourcesanspro}
 - \usepackage{fancyhdr} # modify header into left, center, right
 - \pagestyle{fancy} # cues the use of fancy headers
 - \fancyfoot{} # cues the use of fancy footer
 - \fancyhead[L]{EEC MS Thesis Draft} # month & year on header left 
 - \fancyhead[R]{p. \thepage} # name and page on header right
 - \usepackage{subcaption}
 - \usepackage{float}
# # - \fancyfoot[R]{ }
 - \usepackage{setspace}
 # - doublespacing # manipulate line spacing 
# - \usepackage{parskip} # manipulate indents and spacing before/after paragra phs 
# - \usepackage{xcolor} # changes colors of text
# # http://latexcolor.com/ to choose colors
# # define the colors used above with rgb codes
# - \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
# - \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
# # to center to top level (#) headings (my name) and change color of font
# # more info # https://www.ctan.org/pkg/sectsty
# - \usepackage{sectsty}
# - \sectionfont{\centering\color{darkmidnightblue}}
# # to center to sub-sub-headings (###) and change color of font
# - \usepackage{sectsty} 
# - \subsectionfont{\centering\color{darkmidnightblue}}
# - \usepackage{sectsty} 
# - \subsubsectionfont{\raggedright\color{darkmidnightblue}}
# - \usepackage{wrapfig} 
# - \newcommand{\blandscape}{\begin{landscape}}
# - \newcommand{\elandscape}{\end{landscape}}
# - \usepackage[font=small,labelfont=bf]{caption} #Required for specifying captions to tables and figures
# - \usepackage{indentfirst}
# - \setlength\parindent{22pt} # uncomment if you want indented paragraphs
bibliography: ["eric-thesis.bib"]
output: bookdown::pdf_document2
  # pdf_document:
  #   includes:
  #     # in_header: style/preamble.tex
  #     template: null
  #     keep_tex: no
  #     extra_dependencies: ["float"]
      # number_sections: true
# documentclass: style/nsf2
biblio-style: apalike
csl: ecology.csl
---

@@

FOR TOMORROW:

1) Finish adding citations

2) Stat results: biology first, then stats (e.g., abundance ranged form xxx in rectangular to xxx in winged)

3) Review other papers to find:

- those with similar results
- those with contrary results
- do this with dung bettles AND other insect taxa

DOWN THE ROAD

@@

2025

-----

@@

-----

<!-- _Your dedication is typed here. It should begin with the word “To.” (To my Mom is a typical dedication) If your dedication is longer than a single line it should be single-spaced, and centered vertically and horizontally_ -->

@@

----

**ACKNOWLEDGMENTS**
<!-- _Acknowledgments must be written in complete sentences. Do not use direct address. For example, instead of Thanks, Mom and Dad!, you should say I thank my parents._  -->

@@

----

**LIST OF ABBREVIATIONS**

@@

----

@@

**CHAPTER 1**

**Influence of Connectivity on Dung Beetle Communities**

@@

Dung beetles have emerged as a model system with which to test spatial ecology hypotheses [@ros_how_2012; @roslin_dung_2000].They are an incredibly well studied group of insects which are well known for driving a multitude of ecosystem functions [@hasan_dung_2024]. The removal, breakdown, and burial of animal feces drive important ecosystem interactions provided by dung beetles enhancing nutrient cycling and soil quality, the reduction of breeding sites for parasites, and a reduction in methane emissions from dung [@slade_disentangling_2016; @WOS:000350444300013]. [**EB edit:** I added the following to justify dung veetles more, and then made the questions a second paragraph] Local assemblages of dung beetles can be species-rich with species comprising a broad range of functional traits (e.g., size, foraging style, resource-use) **(citation)**. Previous studies have shown that isolated patches of habitat frequently have lower dung beetle diversity and abundance than areas of continuous habitat, as well as documented their presence in linear strips of habitat that resemble corridors [@WOS:000707546700001].  Past studies have also focused on how landscape structure alters the community compositions of dung beetles[@WOS:000398662200001], yet large landscape scale experimental studies with carefully controlled and replicated treatments are non-existent for this model species.

Here, we aim to gain an understanding of how dung beetles, a group of insects well known for strong dispersal ability in order to compete for ephemeral resources [@hanski_dung_1991], interact with corridors in their landscapes. We sampled dung beetle communities in experimental landscapes developed for the express purposes of comparing connected and isolated patches, as well as the effects of patch area to edge ratio and distance to edge [@tewksbury_corridors_2002]. To ask the questions: (1) How are species abundances of dung beetles distributed within isolated and connected patches and what are their relationships with assemblages in matrix habitat? (2) Does species richness vary when movement between patches is facilitated by movement corridors? (3) Are there shifts in species diversity/composition and what are the implications for ecosystem service functionality?

@@

Our study took place at the Savannah River Site (SRS), a National Environmental Research Park in southern South Carolina, USA (33.208$^\circ$ N, 81.408$^\circ$ W, Figure \@ref(fig:srs-map)).  in four of seven experimental landscapes designed for the purposes of directly observing the impacts of corridors and patch shape on the movements of plants and animals [@tewksbury_corridors_2002]. Each experimental landscape, termed blocks, consists of four patches of open habitat around a central patch all together within a matrix of pine savanna (Figure \@ref(fig:patches)). In each block the central patch (100 $\times$ 100 m) is always connected to one peripheral patch with identical dimensions by a 150 $\times$ 25 m corridor, this will hereafter be referred  to as the connected patch. The remaining patches are either "winged" or "rectangular".  The winged patch is also 100 $\times$ 100 m, however they exhibit their characteristic wings in the form of two 75 $\times$ 25 m offshoots meant to account for the extra area and edge space the corridor provides. The rectangular patch is 100 $\times$ 137.5 m also the same area as the space of the connected patch plus the corridor. Each block has a duplicate of either the winged or rectangle patch, all peripheral patches being 150 m from the center patch. For this study sampling was done in one of each patch type and in one matrix plot per block, all matrix blocks were set up 150 m away from the center as well.

@@

In the months of July and August 2024 dung beetles were sampled in 4 blocks spread across SRS, baited pitfall traps were placed in one of each patch type and in one matrix plot per block (Figure \@ref(fig:pitfalls)). Traps were placed in groups of 3 in the centers of each patch approximately 250 meters from the midpoint of the central patch 40 m from patch edge. Pitfalls were oriented in a triangular pattern with the bottom two traps positioned towards the center patch, each trap 20 m apart. Plots in the matrix were set up in a similar fashion with the center point 250 m from the center placed equidistant between adjacent patches. Individual pitfall traps consisted of two components, a 10cm tall by 8 cm wide cylinder base topped with a funnel with a 10cm wide rim. We sourced pig feces from the University of Florida Swine Barn Unit. Bait was processed into 5cm wide balls and wrapped in a layer of coffee filter material. For each sample period, traps were buried flush with the ground and baited with pig dung between 8-9 pm and picked up 12 hours later, all beetles captured were stored in ethanol for further processing. In total 16 sampling rounds were carried out with 4 rounds per block, 196 samples were collected.

@@

@@

### Beetle Abundance

@@

### Beetle Richness and Diversity

@@

[**EB:** edit: shouldn't this go in the methods?] We used linear mixed-effects models to compare the influence of patch type on both Shannon Diversity and Simpson's indexes, including block as a random effect to account for spatial variation. In both models, the reference level for patch type was Connected.

@@

_Don't repeat results...tell us:_

@@

@@

\newpage
```{r summary-table, echo=FALSE,message = FALSE,warning=FALSE}
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

@@

```{r abundance-patch, echo=FALSE,message = FALSE,warning=FALSE}
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

@@

```{r bray-curtis, echo=FALSE,message = FALSE,warning=FALSE}
btl_spec_patch<- btl_data |>
  pivot_longer(pvin:osyl, names_to = "species", values_to = "n") |>
  group_by(species,patch) |>
  summarise(n=sum(n, na.rm=TRUE)) |>
  arrange(patch,desc(n)) |>
  pivot_wider(values_from=n,names_from=species) |>
  mutate(patch=case_when(
    patch == "c" ~ "Corridor",
    patch == "m" ~ "Matrix",
    patch == "w" ~ "Winged",
    patch == "r" ~ "Rectangle",
    .default = as.character(patch))) |>
  column_to_rownames("patch")

@@

@@

```{r Table-aovMO, echo=FALSE,message = FALSE,warning=FALSE}
aovM0<-read_csv(here("corridor_docs","eric_ms_thesis","tables","aovM0.csv")) %>%
  mutate(term=case_when(
    term == "patch_type" ~ "Patch type",
    .default = as.character(term))) |>
# aovM0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM0
```

```{r Table-MO, echo=FALSE,message = FALSE,warning=FALSE}
M0<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M0.csv")) %>%
  replace_na(list(group=" ")) %>% 
  # need to round numbers above to 4, convert to character, then na_replace
  # replace_na(list(group=" ", std.error="",statistic=" ",p.value = "")) %>% 
# M0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M0
```

```{r Table-aovMO3, echo=FALSE,message = FALSE,warning=FALSE}
aovM3<-read_csv(here("corridor_docs","eric_ms_thesis","tables","aovM3.csv")) %>%
    mutate(term=case_when(
    term == "sp_code" ~ "Species",
    term == "patch_type" ~ "Patch type",
    term == "sp_code:patch_type" ~ "Species x Patch type",
    .default = as.character(term))) |>
# aovM3<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM3.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM3
```

```{r Table-M3, echo=FALSE,message = FALSE,warning=FALSE}
M3<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M3.csv")) %>%
  replace_na(list(group=" ")) %>% 
  # need to round numbers above to 4, convert to character, then na_replace
  # replace_na(list(group=" ", std.error="",statistic=" ",p.value = "")) %>% 
# M3<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M3.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M3
```

```{r Table-M-rich, echo=FALSE,message = FALSE,warning=FALSE}
M_rich<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_rich.csv")) %>%
   mutate(term=case_when(
    term == "patch_typeMatrix" ~ "Patch Type: Matrix",
    term == "patch_typeRectangle" ~ "Patch Type: Rectangle",
    term == "patch_typeWinged" ~ "Patch Type: Winged",
    .default = as.character(term))) |>
# M_rich<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_rich.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Richness Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_rich
```

```{r Table-M-shan, echo=FALSE,message = FALSE,warning=FALSE}
M_shan<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_shan.csv")) %>%
  replace_na(list(group=" ")) %>% 
  # need to round numbers above to 4, convert to character, then na_replace
  # replace_na(list(group=" ", std.error="",statistic=" ",p.value = "")) %>% 
# M_shan<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_shan.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Shannon Diversity Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_shan
```

```{r Table-M-simp, echo=FALSE,message = FALSE,warning=FALSE}
M_simp<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_simp.csv")) %>%
  replace_na(list(group=" ")) %>% 
  # need to round numbers above to 4, convert to character, then na_replace
  # replace_na(list(group=" ", std.error="",statistic=" ",p.value = "")) %>% 
# M_simp<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_simp.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Simpson's Index Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_simp
```

@@

<!-- _A biographical sketch is required of all candidates. The biographical sketch should be in narrative form. Third person, past tense, it typically includes the educational background of the candidate. The author should have replaced this paragraph with their own._ -->
